---
title: "08__mapping_names_and_merging__3"
output: html_document
---


Background

Here I map uniprots and gene names from related databases so they line up - cell proteome, mouse phospho, GSK3i phospho

I also add proteome data to phos data where possible





###Initialise

Packages
```{r}
library(reshape2)
source("..\\scripts/3T3L1_mouse_IR__DF__202104_functions.R")
```


###Load in data
```{r}
load("data/intermediate/phos_3t3/phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef__1.RData")
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped <- phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef
```


###Proteome

Load in data
```{r}
load("data/intermediate/prot_3t3/proteome_raw_3t3_ddamatched.RData")
```


Map proteome genes and uniprots to DIA phospho
```{r}
proteome_raw_3t3_DIA_matched <- proteome_raw_3t3


###Assign old rownames
proteome_raw_3t3_DIA_matched$old_rownames <- rownames(proteome_raw_3t3)

###Make uniprots

#Use Majority.protein.IDs. Difference compared to Protein.IDs. is very little, and with Majority.protein.IDs we get more with only 1 match
proteome_raw_3t3_DIA_matched$new_uniprot <- uniprot_proteome_from_phos_matcher(old_uniprots = proteome_raw_3t3_DIA_matched$uniprot,
                                                            possible_uniprots_col = proteome_raw_3t3_DIA_matched$Majority.protein.IDs,
                                                            destination_uniprots = phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef$uniprot)

###Make gene names
#Take gene name associated with phospho, by matching uniprots
proteome_raw_3t3_DIA_matched$new_gene <- proteome_raw_3t3_DIA_matched$gene
matches_num_vector <- NULL
for (i in 1:nrow(proteome_raw_3t3_DIA_matched)){
  
  temp_uniprot <- proteome_raw_3t3_DIA_matched[i, "new_uniprot"]
  if (temp_uniprot %in%
      phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef$uniprot){
    
    matches_num_vector[i] <- length(unique(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef[which(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef$uniprot ==
                                                             temp_uniprot),
                                                     "gene_name"]))
    #Only assign if exactly one gene match
    if(matches_num_vector[i] == 1){
      
      proteome_raw_3t3_DIA_matched[i, "new_gene"] <- unique(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef[which(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef$uniprot ==
                                                             temp_uniprot),
                                                     "gene_name"])
    #Fuse matches if multiple
    } else if (matches_num_vector[i] > 1){
      proteome_raw_3t3_DIA_matched[i, "new_gene"] <- paste(unique(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef[which(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef$uniprot ==
                                                             temp_uniprot),
                                                     "gene_name"]),
                                                     collapse = "___")
      
    }
      }
}


##Deal with double and triple matches
#None
proteome_raw_3t3_DIA_matched[grep("___",
                       proteome_raw_3t3_DIA_matched$new_gene), ]

##Deal with NAs
#If NA or "", just give old name
#None
proteome_raw_3t3_DIA_matched[which(is.na(proteome_raw_3t3_DIA_matched$new_gene) |
                                     proteome_raw_3t3_DIA_matched$new_gene == ""), ]


###Make new row names, and uniprot and gene
proteome_raw_3t3_DIA_matched$new_rownames <- apply(proteome_raw_3t3_DIA_matched[, c("new_gene",
                                              "new_uniprot")],
                                1,
                                function(x) paste(x, 
                                                  collapse = "_"))
rownames(proteome_raw_3t3_DIA_matched) <- proteome_raw_3t3_DIA_matched$new_rownames
proteome_raw_3t3_DIA_matched$uniprot <- sapply(rownames(proteome_raw_3t3_DIA_matched),
                            function(x) strsplit(x, "_")[[1]][2])
proteome_raw_3t3_DIA_matched$gene <- sapply(rownames(proteome_raw_3t3_DIA_matched),
                            function(x) strsplit(x, "_")[[1]][1])
```


Add to processed proteome data and export
```{r}
###Load in processed proteome data
load("data/intermediate/prot_3t3/proteome_post_analysis_3t3_ddamatched.RData")
proteome_post_analysis_3t3_DIA_matched <- proteome_post_analysis_3t3

###Add in new rownames, uniprots and gene names
proteome_post_analysis_3t3_DIA_matched$old_rownames <- rownames(proteome_post_analysis_3t3)
proteome_post_analysis_3t3_DIA_matched$old_uniprot <- proteome_post_analysis_3t3$uniprot
proteome_post_analysis_3t3_DIA_matched$old_gene <- proteome_post_analysis_3t3$gene
for (i in 1:nrow(proteome_post_analysis_3t3_DIA_matched)){
  
  proteome_post_analysis_3t3_DIA_matched$new_rownames[i] <- 
    rownames(proteome_raw_3t3_DIA_matched[which(proteome_raw_3t3_DIA_matched$old_rownames ==
                                                  proteome_post_analysis_3t3_DIA_matched$old_rownames[i]), ])
}
rownames(proteome_post_analysis_3t3_DIA_matched) <- proteome_post_analysis_3t3_DIA_matched$new_rownames
proteome_post_analysis_3t3_DIA_matched$uniprot <- sapply(rownames(proteome_post_analysis_3t3_DIA_matched),
                                                         function(x) strsplit(x, "_")[[1]][2])
proteome_post_analysis_3t3_DIA_matched$gene <- sapply(rownames(proteome_post_analysis_3t3_DIA_matched),
                                                      function(x) strsplit(x, "_")[[1]][1])

###Export
save(proteome_raw_3t3_DIA_matched,
     file = "output/data/proteome_raw_3t3_DIA_matched.RData")
save(proteome_post_analysis_3t3_DIA_matched,
     file = "output/data/proteome_post_analysis_3t3_DIA_matched.RData")
```


Add proteome data to DIA phos
I map over FCs, pvalues, nlogpvals,  medians, and mean_normalised_mean
```{r}
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, c("CI_GROUPED_FC",
                                             "DEX_GROUPED_FC",
                                             "TNF_GROUPED_FC",
                                             "MPQ_GROUPED_FC",
                                             "AA_GROUPED_FC",
                                             "CI_GROUPED_pval",
                                             "DEX_GROUPED_pval",
                                             "TNF_GROUPED_pval",
                                             "MPQ_GROUPED_pval",
                                             "AA_GROUPED_pval",
                                             "CI_GROUPED_adj_pval",
                                             "DEX_GROUPED_adj_pval",
                                             "TNF_GROUPED_adj_pval",
                                             "MPQ_GROUPED_adj_pval",
                                             "AA_GROUPED_adj_pval",
                                             "CI_GROUPED_nlog_adj_pval",
                                             "DEX_GROUPED_nlog_adj_pval",
                                             "TNF_GROUPED_nlog_adj_pval",
                                             "MPQ_GROUPED_nlog_adj_pval",
                                             "AA_GROUPED_nlog_adj_pval",
                                             "CI_GROUPED_median",
                                             "DEX_GROUPED_median",
                                             "TNF_GROUPED_median",
                                             "MPQ_GROUPED_median",
                                             "AA_GROUPED_median",
                                             "CI_GROUPED_mean_normalised_mean",
                                             "DEX_GROUPED_mean_normalised_mean",
                                             "TNF_GROUPED_mean_normalised_mean",
                                             "MPQ_GROUPED_mean_normalised_mean",
                                             "AA_GROUPED_mean_normalised_mean",
                                             "CTRL_BAS_PROT_2",
                                             "CTRL_BAS_PROT_3",
                                             "CTRL_BAS_PROT_4",
                                             "CTRL_BAS_PROT_5",
                                             "CTRL_BAS_PROT_6",
                                             "CTRL_INS_PROT_1",
                                             "CTRL_INS_PROT_2",
                                             "CTRL_INS_PROT_3",
                                             "CTRL_INS_PROT_4",
                                             "CTRL_INS_PROT_5",
                                             "CI_BAS_PROT_2",
                                             "CI_BAS_PROT_3",
                                             "CI_BAS_PROT_4",
                                             "CI_INS_PROT_1",
                                             "CI_INS_PROT_2",
                                             "CI_INS_PROT_3",
                                             "CI_INS_PROT_4",
                                             "DEX_BAS_PROT_1",
                                              "DEX_BAS_PROT_2",
                                             "DEX_BAS_PROT_3",
                                             "DEX_BAS_PROT_4",
                                             "DEX_INS_PROT_1",
                                             "DEX_INS_PROT_2",
                                             "DEX_INS_PROT_3",
                                             "DEX_INS_PROT_4",
                                              "TNF_BAS_PROT_1",
                                             "TNF_BAS_PROT_2",
                                             "TNF_BAS_PROT_4",
                                             "TNF_INS_PROT_1",
                                             "TNF_INS_PROT_2",
                                             "TNF_INS_PROT_3",
                                             "TNF_INS_PROT_4",
                                             "MPQ_BAS_PROT_1",
                                              "MPQ_BAS_PROT_2",
                                             "MPQ_BAS_PROT_3",
                                             "MPQ_BAS_PROT_4",
                                             "MPQ_INS_PROT_1",
                                             "MPQ_INS_PROT_2",
                                             "MPQ_INS_PROT_3",
                                             "MPQ_INS_PROT_4",
                                             "AA_BAS_PROT_1",
                                              "AA_BAS_PROT_2",
                                             "AA_BAS_PROT_3",
                                             "AA_BAS_PROT_4",
                                             "AA_INS_PROT_1",
                                             "AA_INS_PROT_2",
                                             "AA_INS_PROT_3",
                                             "AA_INS_PROT_4")] <- NA


for (i in 1:nrow(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped)){
  
  if (phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped$gene_uniprot[i] %in%
      rownames(proteome_post_analysis_3t3_DIA_matched)){
        
        phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[i, c("CI_GROUPED_FC",
                                             "DEX_GROUPED_FC",
                                             "TNF_GROUPED_FC",
                                             "MPQ_GROUPED_FC",
                                             "AA_GROUPED_FC",
                                             "CI_GROUPED_pval",
                                             "DEX_GROUPED_pval",
                                             "TNF_GROUPED_pval",
                                             "MPQ_GROUPED_pval",
                                             "AA_GROUPED_pval",
                                             "CI_GROUPED_adj_pval",
                                             "DEX_GROUPED_adj_pval",
                                             "TNF_GROUPED_adj_pval",
                                             "MPQ_GROUPED_adj_pval",
                                             "AA_GROUPED_adj_pval",
                                             "CI_GROUPED_nlog_adj_pval",
                                             "DEX_GROUPED_nlog_adj_pval",
                                             "TNF_GROUPED_nlog_adj_pval",
                                             "MPQ_GROUPED_nlog_adj_pval",
                                             "AA_GROUPED_nlog_adj_pval",
                                             "CI_GROUPED_median",
                                             "DEX_GROUPED_median",
                                             "TNF_GROUPED_median",
                                             "MPQ_GROUPED_median",
                                             "AA_GROUPED_median",
                                             "CI_GROUPED_mean_normalised_mean",
                                             "DEX_GROUPED_mean_normalised_mean",
                                             "TNF_GROUPED_mean_normalised_mean",
                                             "MPQ_GROUPED_mean_normalised_mean",
                                             "AA_GROUPED_mean_normalised_mean",
                                              "CTRL_BAS_PROT_2",
                                             "CTRL_BAS_PROT_3",
                                             "CTRL_BAS_PROT_4",
                                             "CTRL_BAS_PROT_5",
                                             "CTRL_BAS_PROT_6",
                                             "CTRL_INS_PROT_1",
                                             "CTRL_INS_PROT_2",
                                             "CTRL_INS_PROT_3",
                                             "CTRL_INS_PROT_4",
                                             "CTRL_INS_PROT_5",
                                             "CI_BAS_PROT_2",
                                             "CI_BAS_PROT_3",
                                             "CI_BAS_PROT_4",
                                             "CI_INS_PROT_1",
                                             "CI_INS_PROT_2",
                                             "CI_INS_PROT_3",
                                             "CI_INS_PROT_4",
                                             "DEX_BAS_PROT_1",
                                              "DEX_BAS_PROT_2",
                                             "DEX_BAS_PROT_3",
                                             "DEX_BAS_PROT_4",
                                             "DEX_INS_PROT_1",
                                             "DEX_INS_PROT_2",
                                             "DEX_INS_PROT_3",
                                             "DEX_INS_PROT_4",
                                              "TNF_BAS_PROT_1",
                                             "TNF_BAS_PROT_2",
                                             "TNF_BAS_PROT_4",
                                             "TNF_INS_PROT_1",
                                             "TNF_INS_PROT_2",
                                             "TNF_INS_PROT_3",
                                             "TNF_INS_PROT_4",
                                             "MPQ_BAS_PROT_1",
                                              "MPQ_BAS_PROT_2",
                                             "MPQ_BAS_PROT_3",
                                             "MPQ_BAS_PROT_4",
                                             "MPQ_INS_PROT_1",
                                             "MPQ_INS_PROT_2",
                                             "MPQ_INS_PROT_3",
                                             "MPQ_INS_PROT_4",
                                             "AA_BAS_PROT_1",
                                              "AA_BAS_PROT_2",
                                             "AA_BAS_PROT_3",
                                             "AA_BAS_PROT_4",
                                             "AA_INS_PROT_1",
                                             "AA_INS_PROT_2",
                                             "AA_INS_PROT_3",
                                             "AA_INS_PROT_4")] <-
          proteome_post_analysis_3t3_DIA_matched[which(rownames(proteome_post_analysis_3t3_DIA_matched) ==
                                                         phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped$gene_uniprot[i]), c("CI_GROUPED_FC",
                                             "DEX_GROUPED_FC",
                                             "TNF_GROUPED_FC",
                                             "MPQ_GROUPED_FC",
                                             "AA_GROUPED_FC",
                                             "CI_GROUPED_pval",
                                             "DEX_GROUPED_pval",
                                             "TNF_GROUPED_pval",
                                             "MPQ_GROUPED_pval",
                                             "AA_GROUPED_pval",
                                             "CI_GROUPED_adj_pval",
                                             "DEX_GROUPED_adj_pval",
                                             "TNF_GROUPED_adj_pval",
                                             "MPQ_GROUPED_adj_pval",
                                             "AA_GROUPED_adj_pval",
                                             "CI_GROUPED_nlog_adj_pval",
                                             "DEX_GROUPED_nlog_adj_pval",
                                             "TNF_GROUPED_nlog_adj_pval",
                                             "MPQ_GROUPED_nlog_adj_pval",
                                             "AA_GROUPED_nlog_adj_pval",
                                             "CI_GROUPED_median",
                                             "DEX_GROUPED_median",
                                             "TNF_GROUPED_median",
                                             "MPQ_GROUPED_median",
                                             "AA_GROUPED_median",
                                             "CI_GROUPED_mean_normalised_mean",
                                             "DEX_GROUPED_mean_normalised_mean",
                                             "TNF_GROUPED_mean_normalised_mean",
                                             "MPQ_GROUPED_mean_normalised_mean",
                                             "AA_GROUPED_mean_normalised_mean",
                                              "NORMAL_GROUPED_1",
                                             "NORMAL_GROUPED_2",
                                             "NORMAL_GROUPED_3",
                                             "NORMAL_GROUPED_4",
                                             "NORMAL_GROUPED_5",
                                             "NORMAL_GROUPED_6",
                                             "NORMAL_GROUPED_7",
                                             "NORMAL_GROUPED_8",
                                             "NORMAL_GROUPED_9",
                                             "NORMAL_GROUPED_10",
                                             "CI_GROUPED_1",
                                             "CI_GROUPED_2",
                                             "CI_GROUPED_3",
                                             "CI_GROUPED_4",
                                             "CI_GROUPED_5",
                                             "CI_GROUPED_6",
                                             "CI_GROUPED_7",
                                             "DEX_GROUPED_1",
                                              "DEX_GROUPED_2",
                                             "DEX_GROUPED_3",
                                             "DEX_GROUPED_4",
                                             "DEX_GROUPED_5",
                                             "DEX_GROUPED_6",
                                             "DEX_GROUPED_7",
                                             "DEX_GROUPED_8",
                                              "TNF_GROUPED_1",
                                             "TNF_GROUPED_2",
                                             "TNF_GROUPED_3",
                                             "TNF_GROUPED_4",
                                             "TNF_GROUPED_5",
                                             "TNF_GROUPED_6",
                                             "TNF_GROUPED_7",
                                             "MPQ_GROUPED_1",
                                              "MPQ_GROUPED_2",
                                             "MPQ_GROUPED_3",
                                             "MPQ_GROUPED_4",
                                             "MPQ_GROUPED_5",
                                             "MPQ_GROUPED_6",
                                             "MPQ_GROUPED_7",
                                             "MPQ_GROUPED_8",
                                             "AA_GROUPED_1",
                                              "AA_GROUPED_2",
                                             "AA_GROUPED_3",
                                             "AA_GROUPED_4",
                                             "AA_GROUPED_5",
                                             "AA_GROUPED_6",
                                             "AA_GROUPED_7",
                                             "AA_GROUPED_8")]
      }
  
  
}

###Make site normalised to protein
matched_protein_conditions <- gsub("_PROT",
                                   "",
                                   colnames(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped)[grep("_PROT_",
                                                                colnames(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped))])
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, sapply(matched_protein_conditions,
                       function(x){
                         x_split <- strsplit(x, "_")[[1]]
                         return(paste(c(x_split[1],
                                        "_",
                                        x_split[2],
                                        "_",
                                        "PROT_norm_",
                                        x_split[3]),
                                      collapse = ""))
                       })] <-
  phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, matched_protein_conditions] -
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, grep("_PROT_",
                     colnames(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped))]


###Add FCs, means and medians

####INS_vs_BAS FCs


###Function: Makes treatment vs basal FCs for given models
#Data is data, columns of format MODEL_BAS/TREATMENT_n e.g. CTRL_INS_4
#method is "median" or "mean"
#models are models e.g. CTRL, CI, DEX
#bas_treatment are names for basal and treatment e.g. BAS, INS
treatment_vs_bas_logFC_maker <- function(data,
                                         method = "median",
                                         models,
                                         bas_treatment){
      
      ##Set up output
      FC_data <- matrix(NA,
                        nrow = nrow(data),
                        ncol = length(models))
      rownames(FC_data) <- rownames(data)
      colnames(FC_data) <- sapply(models,
                                  function(x) paste(c(x, "_FC"),
                                                    collapse = ""))
      
      ##Iterate over models
      for (j in 1:length(models)){
        
        FC_data[, j] <- apply(data[, grep(paste(c(models[j],
                                                  "_",
                                                  bas_treatment[2],
                                                  "_\\d+"),
                                                collapse = ""),
                                          colnames(data))],
                              1,
                              FUN = method,
                              na.rm = TRUE) - 
          apply(data[, grep(paste(c(models[j],
                                                  "_",
                                                  bas_treatment[1],
                                                  "_\\d+"),
                                  collapse = ""),
                                          colnames(data))],
                              1,
                              FUN = method,
                              na.rm = TRUE)
      }
      
      return(FC_data)
}


###Assign FCs
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, c("CTRL_PROT_norm_FC",
                                      "CI_PROT_norm_FC",
                                      "DEX_PROT_norm_FC",
                                      "TNF_PROT_norm_FC",
                                      "MPQ_PROT_norm_FC",
                                      "AA_PROT_norm_FC")] <- 
  treatment_vs_bas_logFC_maker(data = phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped,
                               method = "median",
                               models = c("CTRL",
           "CI",
           "DEX",
           "TNF",
           "MPQ",
           "AA"),
           bas_treatment = c("BAS_PROT_norm",
                   "INS_PROT_norm"))






####Models vs ctrl


###Function: Makes model vs ctrl FCs
#Data is data, columns of format MODEL_BAS/TREATMENT_n e.g. CTRL_INS_4
#method is "median" or "mean"
#models are models e.g. CI_BAS, DEX_BAS
#control is name for control e.g. CTRL_BAS, CTRL_INS
model_vs_ctrl_logFC_maker <- function(data,
                                      method = "median",
                                      models,
                                      control){


    ##Set up data
    FC_data <- matrix(NA,
                      nrow = nrow(data),
                      ncol = length(models))
    rownames(FC_data) <- rownames(data)
    colnames(FC_data) <- sapply(models,
                                function(x) paste(c(x, "_FC"),
                                                  collapse = ""))
    
    ##Get CTRL medians or (means)
    CTRL_medians <- apply(data[, grep(paste(c(control,
                                              "_\\d+"),
                                            collapse = ""),
                                      colnames(data))],
                          1,
                          FUN = method,
                          na.rm = TRUE)
    
    ##Loop over models
    for (j in 1:length(models)){
      
      FC_data[, j] <- apply(data[, grep(paste(c(models[j],
                                              "_\\d+"),
                                            collapse = ""),
                                      colnames(data))],
                          1,
                          FUN = method,
                          na.rm = TRUE) -
        CTRL_medians
    }
    
    return(FC_data)
}


###Assign FCs
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, c("CI_PROT_norm_FC_on_control_BAS",
           "DEX_PROT_norm_FC_on_control_BAS",
           "TNF_PROT_norm_FC_on_control_BAS",
           "MPQ_PROT_norm_FC_on_control_BAS",
           "AA_PROT_norm_FC_on_control_BAS")] <- 
  model_vs_ctrl_logFC_maker(data = phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped,
                            models = c("CI_BAS_PROT_norm",
                                           "DEX_BAS_PROT_norm",
                                           "TNF_BAS_PROT_norm",
                                           "MPQ_BAS_PROT_norm",
                                           "AA_BAS_PROT_norm"),
                            control = "CTRL_BAS_PROT_norm")
phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, c("CI_PROT_norm_FC_on_control_INS",
           "DEX_PROT_norm_FC_on_control_INS",
           "TNF_PROT_norm_FC_on_control_INS",
           "MPQ_PROT_norm_FC_on_control_INS",
           "AA_PROT_norm_FC_on_control_INS")] <- 
  model_vs_ctrl_logFC_maker(data = phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped,
                            models = c("CI_INS_PROT_norm",
                                           "DEX_INS_PROT_norm",
                                           "TNF_INS_PROT_norm",
                                           "MPQ_INS_PROT_norm",
                                           "AA_INS_PROT_norm"),
                            control = "CTRL_INS_PROT_norm")

###Medians and means

##Make conditions
conditions <- c("CTRL_BAS_PROT_norm",
                "CI_BAS_PROT_norm",
                                           "DEX_BAS_PROT_norm",
                                           "TNF_BAS_PROT_norm",
                                           "MPQ_BAS_PROT_norm",
                                           "AA_BAS_PROT_norm",
                "CTRL_INS_PROT_norm",
                "CI_INS_PROT_norm",
                                           "DEX_INS_PROT_norm",
                                           "TNF_INS_PROT_norm",
                                           "MPQ_INS_PROT_norm",
                                           "AA_INS_PROT_norm")

##Assign medians and mean by looping over conditions
for (i in 1:length(conditions)){
  
  phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, paste(c(conditions[i],
                                              "_mean"),
                                            collapse = "")] <- 
    apply(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, grep(paste(c(conditions[i],
                                                           "_\\d+"),
                                                         collapse = ""),
                                                   colnames(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped))],
          1,
          FUN = "mean",
          na.rm = TRUE)
  phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, paste(c(conditions[i],
                                              "_median"),
                                            collapse = "")] <- 
    apply(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped[, grep(paste(c(conditions[i],
                                                           "_\\d+"),
                                                         collapse = ""),
                                                   colnames(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped))],
          1,
          FUN = "median",
          na.rm = TRUE)
}

save(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped,
     file = "output/data/phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped__3_02.RData")
```



###Export
```{r}
save(phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped,
     file = "output/data/phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped__1.RData")

#Make phos_3t3_proc
phos_3t3_proc <- phos_3t3_filt_norm_imp_below_ds1_looserstats_stats_cols_regdef_mapped
save(phos_3t3_proc,
     file = "output/data/phos_3t3_proc__4.RData")
```

































